Bullet Data Preparation for LIME Diagnostics Paper

### 2020-09-16 code/data-preparation.Rmd
moved the compression of all raw data and static figure to the same document and resaved all data

```{r eval = FALSE}
zip(
  zipfile = "../data/raw/hamby-comparisons.csv.zip", 
  files = "../data/raw/hamby-comparisons.csv"
)
zip(
  zipfile = "../data/bullet-train.csv.zip", 
  files = "../data/bullet-train.csv"
)
```

@@

```{r eval = FALSE}
zip(
  zipfile = "../data/raw/h224-set1-features.rds.zip", 
  files = "../data/raw/h224-set1-features.rds"
)
zip(
  zipfile = "../data/raw/h224-set11-features.rds.zip", 
  files = "../data/raw/h224-set11-features.rds"
)
zip(
  zipfile = "../data/bullet-test.csv.zip", 
  files = "../data/bullet-test.csv"
)
```

@@

```{r eval = FALSE}
zip(
  zipfile = "../data/raw/signatures.rds.zip", 
  files = "../data/raw/signatures.rds"
)
zip(
  zipfile = "../data/example-signatures.csv.zip", 
  files = "../data/example-signatures.csv"
)
```

>>>>

```{r eval = FALSE}
zip(
  zipfile = "../data/bullet-train.csv.zip", 
  files = "../data/bullet-train.csv"
)
```

@@

```{r eval = FALSE}
zip(
  zipfile = "../data/bullet-test.csv.zip", 
  files = "../data/bullet-test.csv"
)
```

@@

```{r eval = FALSE}
zip(
  zipfile = "../data/example-signatures.csv.zip", 
  files = "../data/example-signatures.csv"
)
```
